---
title: "EHR Monthly Dashboard"
author: "Wei Fu"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    social: menu
    source_code: embed
    theme: cosmo
    #theme: united
    #theme: flatly
    vertical_layout: scroll
# runtime: shiny
---

```{r setup, include=FALSE}

library(flexdashboard)
library(highcharter)
library(tidyverse)
library(viridisLite)
library(forecast)
library(treemap)

library(dygraphs)
library(xts)
library(colorspace)
library(lubridate)

library(knitr)
library(kableExtra)
library(scales)


library(ggplot2)
library(plotly)
thm <- 
  hc_theme(
    # colors = c("#1a6ecc", "#434348", "#90ed7d"),
     colors = rainbow_hcl(7),
    # colors = c("#E495A5", "#86B875", "#7DB0DD"),
    chart = list(
      backgroundColor = "transparent",
      style = list(fontFamily = "mono")
      #Source Sans Pro
      #mono
      #Verdana
    ),
    xAxis = list(
      gridLineWidth = 1
    )
  )

library(readxl)

ehrin <- "D:/Projects/EHR/EHR Monthly Data 09152020.xlsx"
comp <- read_excel(ehrin, 
    sheet = "Company Symbol Lookup", col_types = c("text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "date"))
#View(EHR_Metrics_by_Week_09_03)

Metrics <- read_excel(ehrin, 
    sheet = "sql", col_types = c("text", 
        "text", "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "date"))
#View(Metrics)


#join by company symbol to get company name
names(Metrics)[colnames(Metrics) == "primary_member_company_symbol"] <- "Company_Symbol"
names(Metrics)[colnames(Metrics) == "search_date_for_calculation_only"] <- "Request_Month"

cmb<- left_join(Metrics, comp, by="Company_Symbol") 


# library(xlsx)
# write.xlsx(cmb, paste("D:/Projects/EHR/temp", today(), ".xlsx", sep=""))

library(stringr)
#remove space in the column names
names(cmb)<- str_replace_all(names(cmb), c("\\\r\\\n" = "." , "," = "", " "="_" ))
cmb$Request_Month <- as.Date(cmb$Request_Month)
 
# one company may be associated with multiple company symbols.
# Need to group them together
cmb$Company <-ifelse(cmb$Company_Symbol %in% c("16", "16S2S"), "NWM", 
                     ifelse(cmb$Company_Symbol %in% c("75E"), "Pacific_Life",
                     ifelse(cmb$Company_Symbol %in% c("EY", "T93"), "Protective", 
                     ifelse(cmb$Company_Symbol %in% c("LF"), "American_Income",
                     ifelse(cmb$Company_Symbol %in% c("B9", "FD"), "Banner", "Other")))))
cmb$Company_Grp <- ifelse(cmb$Company_Symbol %in% c("16", "16S2S", "75E",
                                                    "EY", "T93", "LF", 
                                                    "B9", "FD"), "Top5", "Other")


# the most recent month
mxm <-max(cmb$Request_Month)

```


Volume
===================================== 


Row {data-height=100}
-----------------------------------------------------------------------

### Current Month

<h2 style="color:grey;text-align:center;"> Month of `r mxm` </h2>

<!-- <p style="color:blue;text-align:center;"> Data as of the Month of `r mxm` </p> -->



Row {data-height=500}
-----------------------------------------------------------------------

### Monthly Request Volumes


```{r}

#grouping by company and filter to last 12 months

cmb2 <- cmb %>%
      filter(difftime(mxm, Request_Month, units = "days") <366) %>%
      group_by(Company_Grp, Request_Month) %>%
      summarise(Volume = sum(`#_request_submitted`), na.rm=FALSE) %>%
      select(Company_Grp, Request_Month, Volume) %>%
      arrange(desc(Request_Month), Company_Grp)

#transpose, fill missing with 0
w<- pivot_wider(cmb2, names_from = Company_Grp, values_from=Volume, values_fill=0)

#reorder the columns to put other to the right
w<- w[, c("Request_Month", "Top5", "Other")]
#w<- w[, c("Request_Month", "American_Income", "NWM", 
#          "Pacific_Life", "Protective", "Banner", "Other")]


# library(describedata)
# wkttl <-proc_means(cmb2[names(cmb2) != "Company"], vars = "Volume", by="Request_date_by_week")
# cmpttl <- proc_means(cmb2, vars = "Volume", by="Company")
############ proc_means has not sum funciton

#get weekly totals. but this requires merging witht he original df
# wkv <- cmb2 %>%
#        group_by(Request_date_by_week) %>%
#        summarise(Weekly_Total=sum(Volume)) %>%
#        arrange(desc(Request_date_by_week))

#creating rowSums
w2 <- w %>%
    mutate(Total = select(., !(Request_Month)) %>% rowSums(na.rm = TRUE))

colttl <- cbind(data.frame(Request_Month=as.Date(0)), data.frame(summarise(w2, across(!(Request_Month), sum))))


w3<-rbind(w2, colttl)
w3$Request_Month <- as.character(w3$Request_Month)
w3[which(as.Date(w3$Request_Month)==as.Date(0)),]$Request_Month <-"Grand Total"

#rmax <- max(as.numeric(rownames(w3)))

w3 %>%
  #mutate(Total=cell_spec(Total, "html", bold=T, italic = T)) %>%
   knitr::kable(caption="Table 1 Top 5 vs. Others Monthly Volume", escape = FALSE, col.names=c("Month", "Top 5", "Other", "Total"),row.names = FALSE, align="c") %>%
   kable_styling(full_width = F, position = "center", fixed_thead = list(enabled = T, background = "#9DECFA"), bootstrap_options=c("striped", "hover", "condensed", "responsive")) %>%
   column_spec(4, bold = F, border_left = T, background = "ivory") %>%
   row_spec(11, bold= T, italic = T, background = "ivory")

```
_Top 5 companies include American Income, Northwest Mutual, Pacific Life, Protective, and Banner by business decision._


### Volume Trend


```{r}
# ```{r, fig.width=4, fig.height=3}


mts<-xts(w2[, -1], as.Date(w2$Request_Month))

mts%>%
dygraph(main = "Monthly Request Volumes", xlab = "Month") %>%
  # dyOptions(stackedGraph = TRUE) %>%
  dyRangeSelector(dateWindow = c("2019-12-01", "2020-12-31")) %>%
  # dyRoller(showRoller = TRUE, rollPeriod = 12) %>%
  dySeries("Top5", label = "Top 5", color = "orangered") %>%
  dySeries("Other", label = "Other", color = "green") %>%
  dySeries("Total", label = "Total", color = "grey")


```



<!-- Row {data-height=600} -->
<!-- ----------------------------------------------------------------------- -->
<!-- ### Volume Trend -->


<!-- ```{r} -->

<!-- ts<- xts(w[, 2:6], as.Date(w$Request_date_by_week)) -->

<!-- #volume chart, multiple series -->
<!-- highchart(type="stock", width = 300) %>%  -->
<!-- #  hc_xAxis(categories=as.Date(index(ts), format="%Y-%m-%d")) %>% -->
<!--   hc_title(text="Volume Trend Over Last 8 Weeks", style=(list(fontFamily = "Helvetica")))  %>% -->
<!--   hc_xAxis(minRange=1) %>% -->
<!--   # hc_add_series(name="2020", data=ma_xts$MA_CUR, dataLabels =list(enabled = TRUE, format='{point.y:.2f}')) %>%  -->
<!--   hc_add_series(name="American Income", data=ts$American_Income, showInLegend = TRUE) %>%  -->
<!--   hc_add_series(name="Northwest Mutual", data=ts$NWM) %>% -->
<!--   hc_add_series(name="Pacific Life", data=ts$Pacific_Life) %>% -->
<!--   hc_add_series(name="Protective", data=ts$Protective) %>% -->
<!--   hc_add_series(name="Other", data=ts$Other) %>% -->
<!--   hc_add_theme(thm) -->

<!--   #  -->
<!--   # hc_annotations( -->
<!--   #   list( -->
<!--   #     labelOptions = list( -->
<!--   #     backgroundColor = 'rgba(255,255,255,0.5)', -->
<!--   #     verticalAlign = 'top', -->
<!--   #     y = 10, -->
<!--   #     shape = "callout", -->
<!--   #     fill = "none" -->
<!--   #   ), -->
<!--   #     labels = list( -->
<!--   #              list(point = list(x =datetime_to_timestamp(as.Date("2020-04-10")), y = 30000, xAxis = 0, yAxis = 0), text = "2020 Good Friday"), -->
<!--   #              list(point = list(x = datetime_to_timestamp(as.Date("2020-05-25")), y = 28000, xAxis = 0, yAxis = 0), text = "2020 Memorial Day") -->
<!--   #     ) -->
<!--   #   ) -->
<!--   # ) %>% -->
<!--   # hc_tooltip(pointFormat = "<span style=\"color:{series.color}\">{series.name}</span>: {point.y:.2f}") %>% -->



<!-- ``` -->


<!-- ### Growth Trend -->

<!-- ```{r} -->

<!-- fn<- function(x) {x*100} -->
<!-- grow3<- grow[which(!is.na(grow$Total)), ] %>% -->
<!--        mutate(across(.cols = !(Request_date_by_week), ~fn(.x))) -->

<!-- ts2<- xts(grow3[, 2:6], as.Date(grow3$Request_date_by_week)) -->

<!-- #volume chart, multiple series -->
<!-- highchart(type="stock") %>%  -->
<!--   # hc_xAxis(categories=as.Date(index(ts2), format="%Y-%m-%d")) %>% -->
<!--   hc_title(text="% Change in Volume Over Last 8 Weeks", style=(list(fontFamily = "Lucida Sans Unicode")))  %>% -->
<!--   hc_xAxis(minRange=1) %>% -->
<!--   hc_yAxis(labels=list(format="{value}%")) %>% -->
<!--   # hc_add_series(name="2020", data=ma_xts$MA_CUR, dataLabels =list(enabled = TRUE, format='{point.y:.2f}')) %>%  -->
<!--   hc_add_series(name="American Income", data=ts2$American_Income, showInLegend = TRUE) %>%  -->
<!--   hc_add_series(name="Northwest Mutual", data=ts2$NWM) %>% -->
<!--   hc_add_series(name="Pacific Life", data=ts2$Pacific_Life) %>% -->
<!--   hc_add_series(name="Protective", data=ts2$Protective) %>% -->
<!--   hc_add_series(name="Other", data=ts2$Other) %>% -->
<!--   hc_add_theme(thm) %>% -->
<!--   hc_tooltip(pointFormat = "<span style=\"color:{series.color}\">{series.name}</span>: {point.y:.2f}%")  -->

<!--   #  -->
<!--   # hc_annotations( -->
<!--   #   list( -->
<!--   #     labelOptions = list( -->
<!--   #     backgroundColor = 'rgba(255,255,255,0.5)', -->
<!--   #     verticalAlign = 'top', -->
<!--   #     y = 10, -->
<!--   #     shape = "callout", -->
<!--   #     fill = "none" -->
<!--   #   ), -->
<!--   #     labels = list( -->
<!--   #              list(point = list(x =datetime_to_timestamp(as.Date("2020-04-10")), y = 30000, xAxis = 0, yAxis = 0), text = "2020 Good Friday"), -->
<!--   #              list(point = list(x = datetime_to_timestamp(as.Date("2020-05-25")), y = 28000, xAxis = 0, yAxis = 0), text = "2020 Memorial Day") -->
<!--   #     ) -->
<!--   #   ) -->
<!--   # ) %>% -->





<!-- ``` -->

<!-- Row {data-height=900} -->
<!-- ----------------------------------------------------------------------- -->

<!-- ### Number of Weeks with No Request -->

<!-- ```{r} -->
<!-- nrq <- cmb %>% -->
<!--        select(Company_Name, Company_Symbol, Request_date_by_week) %>% -->
<!--        group_by(Company_Name, Company_Symbol) %>% -->
<!--        summarise(minwk=min(Request_date_by_week), maxwk=max(Request_date_by_week)) %>% -->
<!--        select(Company_Name, Company_Symbol, minwk, maxwk) %>% -->
<!--        mutate(noreq=(difftime(mwk, maxwk, units = "weeks"))) %>% -->
<!--        filter(noreq >0) %>% -->
<!--        arrange(noreq, Company_Name, Company_Symbol) -->

<!-- class(nrq$noreq) <- "num" -->

<!-- nrq %>% -->
<!--   #mutate(Total=cell_spec(Total, "html", bold=T, italic = T)) %>% -->
<!--    knitr::kable(caption="Table 3 Companies with No Request in Weeks", escape = FALSE, col.names=c("Company", "Company Symbol", "Start Week", "End Week", "Gap"),row.names = TRUE, align="c") %>% -->
<!--    kable_styling(full_width = F, position = "center", fixed_thead = list(enabled = T, background = "#ccfff5"), bootstrap_options=c("striped", "hover", "condensed", "responsive")) %>% -->
<!--    column_spec(6, bold = F, border_left = T, background = "#ffe6e6")  -->

<!-- ``` -->

<!-- ### Weekly Volume vs. Growth -->


<!-- ```{r} -->

<!-- vg <- cmb %>% -->
<!--       filter(difftime(mwk, Request_date_by_week, units = "weeks") <=1) %>% -->
<!--       select(Company_Name, Company_Symbol, Request_date_by_week, `#_request_submitted`) %>% -->
<!--       group_by(Company_Name, Company_Symbol) %>% -->
<!--       mutate(Lst_wk_req=lead(`#_request_submitted`, n=1L)) %>% -->
<!--       mutate(wkly_chg = (`#_request_submitted`/Lst_wk_req)-1) %>% -->
<!--       filter(Request_date_by_week == mwk) %>% -->
<!--       arrange(desc(wkly_chg)) -->

<!-- vg$wkly_chg_pct <- percent_format(accuracy = 0.1)(vg$wkly_chg) -->


<!-- vg[, !(names(vg) %in% c("Request_date_by_week", "wkly_chg"))] %>% -->
<!--   #mutate(Total=cell_spec(Total, "html", bold=T, italic = T)) %>% -->
<!--    knitr::kable(caption="Table 4 Lastest Weekly Volume vs. Weekly Growth by Company", escape = FALSE, col.names=c("Company", "Symbol", "Current Week", "Prior Week", "Growth"),row.names = TRUE, align="c") %>% -->
<!--    kable_styling(full_width = F, position = "center", fixed_thead = list(enabled = T, background = "#ccfff5"), bootstrap_options=c("striped", "hover", "condensed", "responsive")) %>% -->
<!--    column_spec(6, bold = F, border_left = T, background = "#ffe6ff")  -->


<!-- ``` -->

<!-- Row {data-height=800} -->
<!-- ----------------------------------------------------------------------- -->

<!-- ### Volume vs Growth Chart -->

<!-- _Volumes above the average are categorized as large. Changes greater than 0 are categorized as growth._ -->

<!-- ```{r fig.height=3, fig.width=8, fig.align = "center", out.width='40%'} -->

<!-- wavg <- mean(vg$`#_request_submitted`) -->

<!-- vg$Segment <- ifelse(vg$`#_request_submitted` >= wavg, ifelse(vg$wkly_chg_pct >0, "Large Growing", "Large Not Growing"), ifelse(vg$wkly_chg_pct>0, "Small Growing", "Small Not Growing") ) -->

<!-- p <- ggplot(vg[which(!is.na(vg$wkly_chg_pct)),], aes(x=`#_request_submitted`, y=wkly_chg, color=Segment, text=Company_Name)) + -->
<!--            geom_point(shape=1)+      # Use hollow circles -->
<!--            labs( -->
<!--                 x = "Current Week Volume", -->
<!--                 y = "Change Over Prior Week", -->
<!--                 color = "Segment") + -->
<!--            scale_y_continuous(labels = scales::percent_format(accuracy = 1))  -->

<!-- ggplotly(p, tooltip = c("text", "color")) -->
<!-- # pp<-ggplotly(p, width=400, height=500) -->

<!-- # library(htmltools) -->
<!-- # ppc <- htmltools::div( pp, align="center" ) -->

<!-- ``` -->


<!-- Hit Rate -->
<!-- =====================================  -->

<!-- Row {data-height=600} -->
<!-- ----------------------------------------------------------------------- -->
<!-- ### Hit Rate by Vendor -->

<!-- ```{r} -->


<!-- ``` -->
