---
title: "EHR Dashboard"
author: "Wei Fu"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    social: menu
    source_code: embed
    theme: flatly
    #theme: united
    #theme: cosmo
    vertical_layout: scroll
# runtime: shiny
---

```{r setup, include=FALSE}

library(flexdashboard)
library(highcharter)
library(tidyverse)
library(viridisLite)
library(forecast)
library(treemap)

library(dygraphs)
library(xts)
library(colorspace)
library(lubridate)

library(knitr)
library(kableExtra)
library(scales)


library(ggplot2)
library(plotly)
library(data.table)

thm <- 
  hc_theme(
    # colors = c("#1a6ecc", "#434348", "#90ed7d"),
     colors = rainbow_hcl(7),
    # colors = c("#E495A5", "#86B875", "#7DB0DD"),
    chart = list(
      backgroundColor = "transparent",
      style = list(fontFamily = "mono")
      #Source Sans Pro
      #mono
      #Verdana
    ),
    xAxis = list(
      gridLineWidth = 1
    )
  )

library(readxl)

ehrin <- "D:/Projects/EHR/Weekly/weekly_10112020.xlsx"
comp <- read_excel(ehrin, 
    sheet = "Company Symbol Lookup", col_types = c("text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "blank"))


Metrics <- read_excel(ehrin, 
    sheet = "company", col_types = c("text", 
        "date", "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "blank"))

Vendor <- read_excel(ehrin, 
    sheet = "vendor", col_types = c("text", "text",
        "date", "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "blank"))

ds <- read_excel(ehrin, 
    sheet = "data_source", col_types = c("text", "text","text",
        "date", "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric"))

# use "skip" instead of "blank"

#join by company symbol to get company name
names(Metrics)[colnames(Metrics) == "primary_member_company_symbol"] <- "Company_Symbol"

library(data.table)
cmb<- left_join(Metrics, comp, by="Company_Symbol") %>%
      filter(!(Company_Symbol %ilike% "^MIB" | Company_Symbol %ilike% "PEN$"))


# library(xlsx)
# write.xlsx(cmb, paste("D:/Projects/EHR/temp", today(), ".xlsx", sep=""))

library(stringr)
#remove space in the column names
names(cmb)<- str_replace_all(names(cmb), c("\\\r\\\n" = "." , "," = "", " "="_" ))
cmb$Request_date_by_week <- as.Date(cmb$Request_date_by_week)
 
# one company may be associated with multiple company symbols.
# Need to group them together
cmb$Company <-ifelse(cmb$Company_Symbol %in% c("16", "16S2S"), "NWM", 
                     ifelse(cmb$Company_Symbol %in% c("75E"), "Pacific_Life",
                     ifelse(cmb$Company_Symbol %in% c("EY", "T93"), "Protective", 
                     ifelse(cmb$Company_Symbol %in% c("LF"), "American_Income",
                     ifelse(cmb$Company_Symbol %in% c("B9", "FD"), "Banner", "Other")))))


# the most recent week
mwk <-as.Date(ifelse(difftime(today(),max(cmb$Request_date_by_week), units = "days") <7, max(cmb$Request_date_by_week)-7, max(cmb$Request_date_by_week)))



Vendor$request_date_by_week <- as.Date(Vendor$request_date_by_week)


#join by company symbol to get company name
names(Vendor)[colnames(Vendor) == "company_code"] <- "Company_Symbol"

library(data.table)
cvdr<- left_join(Vendor, comp, by="Company_Symbol") %>%
      filter(!(Company_Symbol %ilike% "^MIB" | Company_Symbol %ilike% "PEN$"))


# one company may be associated with multiple company symbols.
# Need to group them together
cvdr$Company <-ifelse(cvdr$Company_Symbol %in% c("16", "16S2S"), "NWM", 
                     ifelse(cvdr$Company_Symbol %in% c("75E"), "Pacific_Life",
                     ifelse(cvdr$Company_Symbol %in% c("EY", "T93"), "Protective", 
                     ifelse(cvdr$Company_Symbol %in% c("LF"), "American_Income",
                     ifelse(cvdr$Company_Symbol %in% c("B9", "FD"), "Banner", "Other")))))

```



Hit
===================================== 



Row {data-height=100}
-----------------------------------------------------------------------

### Current Week

<h2 style="color:grey;text-align:center;"> Week Beginning On `r mwk` </h2>

<!-- <p style="color:blue;text-align:center;"> Data as of the week of `r mwk` </p> -->



Row {.tabset .tabset-fade .tabset-dropdown data-height=600}
-----------------------------------------------------------------------

### Vendor Request and Release Stats

<!-- ```{r} -->
<!-- ehrw <- "D:/Projects/EHR/Weekly/EHR_CVS_Weekly_10022020.xlsx" -->
<!-- comp2 <- read_excel(ehrw,  -->
<!--     sheet = "Company Symbol Lookup", col_types = c("text",  -->
<!--         "text", "text", "text", "text", "text",  -->
<!--         "text", "text", "blank")) -->

<!-- Metrics2 <- read_excel(ehrw,  -->
<!--     sheet = "Company_Vendor", col_types = c("text",  -->
<!--         "text", "text", "date", "numeric",  -->
<!--         "numeric", "numeric", "numeric",  -->
<!--         "numeric", "numeric", "numeric")) -->



<!-- #join by company symbol to get company name -->
<!-- names(Metrics2)[colnames(Metrics2) == "company_code"] <- "Company_Symbol" -->

<!-- cmbn<- left_join(Metrics2, comp2, by="Company_Symbol")  -->


<!-- names(cmbn)<- str_replace_all(names(cmbn), c("\\\r\\\n" = "." , "," = "", " "="_" )) -->
<!-- cmbn$request_date_by_week <- as.Date(cmbn$request_date_by_week) -->

<!-- # one company may be associated with multiple company symbols. -->
<!-- # Need to group them together -->
<!-- cmbn$Company <-ifelse(cmbn$Company_Symbol %in% c("16", "16S2S"), "NWM",  -->
<!--                      ifelse(cmbn$Company_Symbol %in% c("75E"), "Pacific_Life", -->
<!--                      ifelse(cmbn$Company_Symbol %in% c("EY", "T93"), "Protective",  -->
<!--                      ifelse(cmbn$Company_Symbol %in% c("LF"), "American_Income", -->
<!--                      ifelse(cmbn$Company_Symbol %in% c("B9", "FD"), "Banner", "Other"))))) -->

<!-- #grouping by vendor and filter to last 8 weeks -->
<!-- mwk2 <-max(cmbn$request_date_by_week) -->

<!-- cmbn2 <- cmbn %>% -->
<!--       filter((mwk2 - request_date_by_week) <56) %>% -->
<!--       group_by(vendor_name, request_date_by_week) %>% -->
<!--       summarise(Request = sum(num_request_submitted, na.rm=FALSE), Hit=sum(num_records_found), -->
<!--                 Release = sum(num_records_released)) %>% -->
<!--       mutate(Hit_Rate=Hit/Request, Release_Rate = Release/Request) %>% -->
<!--       select(vendor_name, request_date_by_week, Request, Hit_Rate, Release_Rate) %>% -->
<!--       arrange(desc(request_date_by_week), vendor_name) -->

<!-- #transpose, fill missing with 0 -->
<!-- v<- pivot_wider(cmbn2, names_from = vendor_name, names_sort = TRUE, names_glue = "{vendor_name}_{.value}", values_from=c(Request, Hit_Rate, Release_Rate), values_fill=0)  -->

<!-- names(v)<- str_replace_all(names(v), c("\\\r\\\n" = "." , "," = "", " "="_" )) -->

<!-- v_temp <- v[, names(v) != "request_date_by_week"] -->
<!-- v <- cbind(v[, "request_date_by_week"], v_temp[, order(colnames(v_temp))]) -->

<!-- #reorder the columns to put other to the right -->
<!-- # w<- w[, c("Request_date_by_week", "American_Income", "NWM",  -->
<!-- #           "Pacific_Life", "Protective", "Other")] -->



<!-- #creating rowSums -->
<!-- v2 <- v %>% -->
<!--     mutate(TotalRequest = select(., ends_with("Request")) %>% rowSums(na.rm = TRUE)) -->

<!-- colttl <- cbind(data.frame(request_date_by_week=as.Date(0)), data.frame(summarise(v2, across(ends_with("Request"), sum)))) -->

<!-- library(data.table) -->
<!-- v3<-rbind(v2[, colnames(v2) %like% "Request" | colnames(v2) %like% "request"], colttl) -->


<!-- v4<- left_join(v3, v2[, !(colnames(v2) %like% "Request")], by="request_date_by_week")  -->

<!-- v_temp <- v4[, !(names(v4) %in% c("request_date_by_week", "TotalRequest"))] -->
<!-- v5 <- cbind(v4["request_date_by_week"], v_temp[, order(colnames(v_temp))], v4["TotalRequest"]) -->

<!-- v5$request_date_by_week <- as.character(v5$request_date_by_week) -->
<!-- v5[which(as.Date(v3$request_date_by_week)==as.Date(0)),]$request_date_by_week <-"Grand Total" -->

<!-- #rmax <- max(as.numeric(rownames(w3))) -->

<!-- v6 <- v5 %>% -->
<!--        mutate(across(.cols = !contains("request") & !contains("Request"), ~percent_format(accuracy = 0.1)(.x))) -->

<!-- v6 %>% -->
<!--   #mutate(Total=cell_spec(Total, "html", bold=T, italic = T)) %>% -->
<!--    knitr::kable(caption="Table 1 Vendor Performance", escape = FALSE, col.names=c("Week",  -->
<!--                 "Hit Rate", "Release Rate", "Search",  -->
<!--                 "Hit Rate", "Release Rate", "Search", -->
<!--                 "Hit Rate", "Release Rate", "Search", -->
<!--                 "Hit Rate", "Release Rate", "Search", -->
<!--                 "Hit Rate", "Release Rate", "Search", "Search Total"),row.names = FALSE, align="c") %>% -->
<!--    add_header_above(c(" " = 1, "Epic"=3, "Healthx"=3, "Midwest Health"=3, -->
<!--                       "UHIN"=3, "Veradigm"=3, " "=1)) %>% -->
<!--    kable_styling(full_width = F, position = "center", fixed_thead = list(enabled = T, background = "#ccffe6"), bootstrap_options=c("striped", "hover", "condensed", "responsive")) %>% -->
<!--    column_spec(17, bold = F, border_left = T, background = "ivory") %>% -->
<!--    row_spec(9, bold= T, italic = T, background = "ivory") -->



<!-- ``` -->

```{r}




cmbn2 <- cvdr %>%
      filter( (mwk - request_date_by_week) <56 & (mwk - request_date_by_week) >=0 & !(Company_Symbol %ilike% "^MIB" | Company_Symbol %ilike% "PEN$")) %>%
      group_by(vendor_name, request_date_by_week) %>%
      summarise(Request = sum(num_request_submitted, na.rm=FALSE),                                                     Hit=sum(num_requests_with_one_or_more_records_found),                                                  Req_w_Rls=sum(num_requests_with_one_or_more_records_released),
                Release = sum(num_records_released)) %>%
      mutate(Hit_Rate=Hit/Request, Release_Rate=Req_w_Rls/Request, Avg_Rls_Req = Release/Req_w_Rls) %>%
      select(vendor_name, request_date_by_week, Request, Hit, Release, Req_w_Rls, Hit_Rate, Release_Rate, Avg_Rls_Req) %>%
      arrange(desc(request_date_by_week), vendor_name)


#transpose, fill missing with 0
v<- pivot_wider(cmbn2, names_from = vendor_name, names_sort = TRUE, names_glue = "{vendor_name}_{.value}", values_from=c(Request, Hit, Release, Req_w_Rls, Hit_Rate, Release_Rate, Avg_Rls_Req), values_fill=0)

names(v)<- str_replace_all(names(v), c("\\\r\\\n" = "." , "," = "", " "="_" ))

v_temp <- v[, names(v) != "request_date_by_week"]
v <- cbind(v[, "request_date_by_week"], v_temp[, order(colnames(v_temp))])



#creating rowSums
# v2 <- v %>%
#     mutate(TotalRequest = select(., ends_with("Request")) %>% rowSums(na.rm = TRUE)) %>% 
#     mutate(TotalReqRls = select(., ends_with("Rls")) %>% rowSums(na.rm = TRUE)) %>% 
#     mutate(TotalRelease = select(., ends_with("Release")) %>% rowSums(na.rm = TRUE)) 

# create totals for each vendor
vttl <- cmbn2 %>%
        group_by(vendor_name) %>%
        summarise(across(Request:Req_w_Rls, sum)) %>%
        mutate(Hit_Rate=Hit/Request, Release_Rate=Req_w_Rls/Request, 
               Avg_Rls_Req = Release/Req_w_Rls) %>%
        arrange(vendor_name)

vtw<- pivot_wider(vttl, names_from = vendor_name, names_sort = TRUE, names_glue = "{vendor_name}_{.value}", values_from=c(Request, Hit, Release, Req_w_Rls, Hit_Rate, Release_Rate, Avg_Rls_Req), values_fill=0)

names(vtw)<- str_replace_all(names(vtw), c("\\\r\\\n" = "." , "," = "", " "="_" ))

vtw <- vtw[, order(colnames(vtw))]

colttl <- cbind(data.frame(request_date_by_week=as.Date(0)), vtw)

library(data.table)
# v3<-rbind(v2[, colnames(v2) %ilike% "^request"| colnames(v2) %ilike% "Request$" | colnames(v2) %ilike% "Rls$" | colnames(v2) %ilike% "Release$"], colttl)
# ^ means beginning with, $ means ending with

v3 <- rbind(v, colttl)


v3$request_week <- as.character(v3$request_date_by_week)
v3[which(as.Date(v3$request_week)==as.Date(0)),]$request_week <-"Grand Total"

v3 <- cbind(v3["request_week"], v3[, !(colnames(v3) %ilike% "week$")])

#rmax <- max(as.numeric(rownames(w3)))

v4 <- v3 %>%
       mutate(across(.cols = ends_with("Rate"), ~percent_format(accuracy = 1)(.x))) %>%
       mutate(across(.cols = ends_with("Avg_Rls_Req"), ~round(.x, digits = 1))) %>%
       select(!ends_with(c("Hit", "Release", "Rls")))

v4 %>%
  #mutate(Total=cell_spec(Total, "html", bold=T, italic = T)) %>%
   knitr::kable(caption="Table 1 Vendor Performance", escape = FALSE, col.names=c("Week",
                "Avg Release", "Hit Rate", "Release Rate", "Request",
                "Avg Release", "Hit Rate", "Release Rate", "Request",
                "Avg Release", "Hit Rate", "Release Rate", "Request",
                "Avg Release", "Hit Rate", "Release Rate", "Request",
                "Avg Release", "Hit Rate", "Release Rate", "Request"),row.names = FALSE, align="c") %>%
   add_header_above(c(" " = 1, "Epic"=4, "Healthx"=4, "Midwest Health"=4,
                      "UHIN"=4, "Veradigm"=4)) %>%
   kable_styling(full_width = F, position = "center", fixed_thead = list(enabled = T, background = "#ccffe6"), bootstrap_options=c("striped", "hover", "condensed", "responsive")) %>%
#   column_spec(17, bold = F, border_left = T, background = "ivory") %>%
   row_spec(9, bold= T, italic = T, background = "ivory")



```

<center> **Definitions**</center>

<center> _Request:	Original applicants a company submits for search_ </center> 
<center> _Hit:	The result of a search if it finds a match_</center> 
<center> _Release:	A record delivered back to the requester_</center> 


### Company Hit and Release Stats

```{r}

chr <- cmb %>%
      filter( (mwk - Request_date_by_week) <56 & (mwk - Request_date_by_week) >=0) %>%
      group_by(Company, Request_date_by_week) %>%
      summarise(Request = sum(`#_request_submitted`, na.rm=FALSE),                                                     Hit=sum(`#_requests_with_1_or_more_Records_Found`),                                                  Req_w_Rls=sum(`#_requests_with_1_or_more_Records_Released`),
                Release = sum(`#_Records_Released`)) %>%
      mutate(Hit_Rate=Hit/Request, Release_Rate=Req_w_Rls/Request, Avg_Rls_Req = Release/Req_w_Rls) %>%
      select(Company, Request_date_by_week, Request, Hit, Release, Req_w_Rls, Hit_Rate, Release_Rate, Avg_Rls_Req) %>%
      arrange(desc(Request_date_by_week), Company)



#transpose, fill missing with 0
v<- pivot_wider(chr, names_from = Company, names_sort = TRUE, names_glue = "{Company}_{.value}", values_from=c(Request, Hit, Release, Req_w_Rls, Hit_Rate, Release_Rate, Avg_Rls_Req), values_fill=0)

names(v)<- str_replace_all(names(v), c("\\\r\\\n" = "." , "," = "", " "="_" ))

v_temp <- v[, names(v) != "Request_date_by_week" & !(colnames(v) %ilike% "^Other")]
v <- cbind(v["Request_date_by_week"], v_temp[, order(colnames(v_temp))], v[, colnames(v) %ilike% "^Other"])


# create totals for each company
vttl <- chr %>%
        group_by(Company) %>%
        summarise(across(Request:Req_w_Rls, sum)) %>%
        mutate(Hit_Rate=Hit/Request, Release_Rate=Req_w_Rls/Request, 
               Avg_Rls_Req = Release/Req_w_Rls) %>%
        arrange(Company)

vtw<- pivot_wider(vttl, names_from = Company, names_sort = TRUE, names_glue = "{Company}_{.value}", values_from=c(Request, Hit, Release, Req_w_Rls, Hit_Rate, Release_Rate, Avg_Rls_Req), values_fill=0)

names(vtw)<- str_replace_all(names(vtw), c("\\\r\\\n" = "." , "," = "", " "="_" ))

vtw <- vtw[, order(colnames(vtw))]

colttl <- cbind(data.frame(Request_date_by_week=as.Date(0)), vtw)


# v3<-rbind(v2[, colnames(v2) %ilike% "^request"| colnames(v2) %ilike% "Request$" | colnames(v2) %ilike% "Rls$" | colnames(v2) %ilike% "Release$"], colttl)
# ^ means beginning with, $ means ending with

v3 <- rbind(v, colttl)


v3$request_week <- as.character(v3$Request_date_by_week)
v3[which(as.Date(v3$request_week)==as.Date(0)),]$request_week <-"Grand Total"

v3 <- cbind(v3["request_week"], v3[, !(colnames(v3) %ilike% "week$")])

#rmax <- max(as.numeric(rownames(w3)))

v4 <- v3 %>%
       mutate(across(.cols = ends_with("Rate"), ~percent_format(accuracy = 1)(.x))) %>%
       mutate(across(.cols = ends_with("Avg_Rls_Req"), ~round(.x, digits = 1))) %>%
       select(!ends_with(c("Hit", "Release", "Rls")))

v4 %>%
  #mutate(Total=cell_spec(Total, "html", bold=T, italic = T)) %>%
   knitr::kable(caption="Table 2 Company Performance", escape = FALSE, col.names=c("Week",
                "Avg Release", "Hit Rate", "Release Rate", "Request",
                "Avg Release", "Hit Rate", "Release Rate", "Request",
                "Avg Release", "Hit Rate", "Release Rate", "Request",
                "Avg Release", "Hit Rate", "Release Rate", "Request",
                "Avg Release", "Hit Rate", "Release Rate", "Request",
                "Avg Release", "Hit Rate", "Release Rate", "Request"),row.names = FALSE, align="c") %>%
   add_header_above(c(" " = 1, "American Income"=4, "Banner"=4, "NWM"=4,
                      "Pacific Life"=4, "Protective"=4, "Other"=4)) %>%
   kable_styling(full_width = F, position = "center", fixed_thead = list(enabled = T, background = "#ccffe6"), bootstrap_options=c("striped", "hover", "condensed", "responsive")) %>%
#   column_spec(17, bold = F, border_left = T, background = "ivory") %>%
   row_spec(9, bold= T, italic = T, background = "ivory")


```


### Company by Vendor 

```{r}

cvdr$Company2 <-ifelse(cvdr$Company_Symbol %in% c("16", "16S2S"), "NWM", 
                     ifelse(cvdr$Company_Symbol %in% c("75E"), "Pacific_Life",
                     ifelse(cvdr$Company_Symbol %in% c("EY", "T93"), "Protective", 
                     ifelse(cvdr$Company_Symbol %in% c("LF"), "American_Income",
                     ifelse(cvdr$Company_Symbol %in% c("B9", "FD"), "Banner", 
                     ifelse(cvdr$Company_Symbol %in% c("SI"), "Country Life", 
                     ifelse(cvdr$Company_Symbol %in% c("H22", "A66"), "SBLI", "Other")))))))

cvdr2 <- cvdr %>%
      filter( (mwk - request_date_by_week) ==0 & !(Company_Symbol %ilike% "^MIB" | Company_Symbol %ilike% "PEN$")) %>%
      group_by(Company2, vendor_name, request_date_by_week) %>%
      summarise(Request = sum(num_request_submitted, na.rm=FALSE),                                                     Hit=sum(num_requests_with_one_or_more_records_found),                                                  Req_w_Rls=sum(num_requests_with_one_or_more_records_released),
                Release = sum(num_records_released)) %>%
      mutate(Hit_Rate=Hit/Request, Release_Rate=Req_w_Rls/Request, Avg_Rls_Req = Release/Req_w_Rls) %>%
      select(Company2, vendor_name, request_date_by_week, Request, Hit, Release, Req_w_Rls, Hit_Rate, Release_Rate, Avg_Rls_Req) %>%
      arrange(desc(request_date_by_week), Company2, vendor_name)


#transpose, fill missing with 0
v<- pivot_wider(cvdr2, names_from = vendor_name, names_sort = TRUE, names_glue = "{vendor_name}_{.value}", values_from=c(Request, Hit, Release, Req_w_Rls, Hit_Rate, Release_Rate, Avg_Rls_Req), values_fill=0)

names(v)<- str_replace_all(names(v), c("\\\r\\\n" = "." , "," = "", " "="_" ))

v_temp <- v[, names(v) != "request_date_by_week"]
# v <- cbind(v[, "request_date_by_week"], v_temp[, order(colnames(v_temp))])
v <- v_temp[, order(colnames(v_temp))]


# create totals for each vendor
 vttl <- cvdr2 %>%
        group_by(vendor_name) %>%
        summarise(across(Request:Req_w_Rls, sum)) %>%
        mutate(Hit_Rate=Hit/Request, Release_Rate=Req_w_Rls/Request,
               Avg_Rls_Req = Release/Req_w_Rls) %>%
        arrange(vendor_name)

vtw<- pivot_wider(vttl, names_from = vendor_name, names_sort = TRUE, names_glue = "{vendor_name}_{.value}", values_from=c(Request, Hit, Release, Req_w_Rls, Hit_Rate, Release_Rate, Avg_Rls_Req), values_fill=0)

names(vtw)<- str_replace_all(names(vtw), c("\\\r\\\n" = "." , "," = "", " "="_" ))

vtw$Company2 <- "Grand Total"
vtw <- vtw[, order(colnames(vtw))]

v3 <- rbind(v, vtw)

# colttl <- cbind(data.frame(request_date_by_week=as.Date(0)), vtw)
# 
# v3 <- rbind(v, colttl)


# v3$request_week <- as.character(v3$request_date_by_week)
# v3[which(as.Date(v3$request_week)==as.Date(0)),]$request_week <-"Grand Total"
# 
# Putting request week in the first position
# v3 <- cbind(v3["request_week"], v3[, !(colnames(v3) %ilike% "week$")])


v4 <- v3 %>%
       mutate(across(.cols = ends_with("Rate"), ~percent_format(accuracy = 1)(.x))) %>%
       mutate(across(.cols = ends_with("Avg_Rls_Req"), ~round(.x, digits = 1))) %>%
       select(!ends_with(c("Hit", "Release", "Rls")))

v4 %>%
  #mutate(Total=cell_spec(Total, "html", bold=T, italic = T)) %>%
   knitr::kable(caption="Table 3 Vendor Performance by Company", escape = FALSE,                                   col.names=c("Company",
                "Avg Release", "Hit Rate", "Release Rate", "Request",
                "Avg Release", "Hit Rate", "Release Rate", "Request",
                "Avg Release", "Hit Rate", "Release Rate", "Request",
                "Avg Release", "Hit Rate", "Release Rate", "Request",
                "Avg Release", "Hit Rate", "Release Rate", "Request"),
                row.names = FALSE, align="c") %>%
   add_header_above(c(" " = 1, "Epic"=4, "Healthx"=4, "Midwest Health"=4,
                      "UHIN"=4, "Veradigm"=4)) %>%
   kable_styling(full_width = F, position = "center", fixed_thead = list(enabled = T, background = "#ccffe6"), bootstrap_options=c("striped", "hover", "condensed", "responsive")) %>%
#   column_spec(17, bold = F, border_left = T, background = "ivory") %>%
   row_spec(8, bold= T, italic = T, background = "ivory")


```

<p style="color:blue;text-align:center;"> Data for the week of `r mwk` only </p>






Row {data-height=800}
-----------------------------------------------------------------------

### Vendor Current Week Position

_The size of the dot represents the request volume of a vendor._

```{r fig.height=5, fig.width=6, fig.align = "center", out.width='40%'}


vdr <- cmbn2 %>%
      filter(request_date_by_week==mwk)

# wavg <- mean(vg$`#_request_submitted`)
# 
# vg$Segment <- ifelse(vg$`#_request_submitted` >= wavg, ifelse(vg$wkly_chg_pct >0, "Large Growing", "Large Not Growing"), ifelse(vg$wkly_chg_pct>0, "Small Growing", "Small Not Growing") )

p2 <- ggplot(vdr, aes(x=Hit_Rate, y=Release_Rate, size=Request, color=Request, text=vendor_name)) +
           geom_point(shape=16)+      # Use dots
           labs(
                title ="Hit Rate vs. Release Rate",
                x = "Current Week Hit Rate",
                y = "Current Week Release Rate",
                color = "Request Size"
                ) +
           scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
           scale_x_continuous(labels = scales::percent_format(accuracy = 1)) 
           # theme_classic()

# pp<-ggplotly(p, width=400, height=500)
ggplotly(p2, tooltip = c("text", "color")) %>%
   layout(xaxis = list(title="Current Week Release Rate"))


# library(htmltools)
# ppc <- htmltools::div( pp, align="center" )

```


<!-- Row {data-height=600} -->
<!-- ----------------------------------------------------------------------- -->

<!-- ### Company vs. Vendor -->





Volume
=====================================


Row {data-height=100}
-----------------------------------------------------------------------

### Current Week

<h2 style="color:grey;text-align:center;"> Week Beginning On `r mwk` </h2>

<!-- <p style="color:blue;text-align:center;"> Data as of the week of `r mwk` </p> -->



Row {data-height=500}
-----------------------------------------------------------------------

### Weekly Request Volumes


```{r}

#grouping by company and filter to last 8 weeks

cmb2 <- cmb %>%
      filter((mwk- Request_date_by_week) <56 & (mwk- Request_date_by_week) >=0 ) %>%
      group_by(Company, Request_date_by_week) %>%
      summarise(Volume = sum(`#_request_submitted`), na.rm=FALSE) %>%
      select(Company, Request_date_by_week, Volume) %>%
      arrange(desc(Request_date_by_week), Company)

#transpose, fill missing with 0
w<- pivot_wider(cmb2, names_from = Company, values_from=Volume, values_fill=0)

#reorder the columns to put other to the right
#w<- w[, c("Request_date_by_week", "American_Income", "NWM",
#          "Pacific_Life", "Protective", "Other")]
w<- w[, c("Request_date_by_week", "American_Income", "NWM",
          "Pacific_Life", "Protective", "Banner", "Other")]


# library(describedata)
# wkttl <-proc_means(cmb2[names(cmb2) != "Company"], vars = "Volume", by="Request_date_by_week")
# cmpttl <- proc_means(cmb2, vars = "Volume", by="Company")
############ proc_means has not sum funciton

#get weekly totals. but this requires merging witht he original df
# wkv <- cmb2 %>%
#        group_by(Request_date_by_week) %>%
#        summarise(Weekly_Total=sum(Volume)) %>%
#        arrange(desc(Request_date_by_week))

#creating rowSums
w2 <- w %>%
    mutate(Total = select(., !(Request_date_by_week)) %>% rowSums(na.rm = TRUE))

colttl <- cbind(data.frame(Request_date_by_week=as.Date(0)), data.frame(summarise(w2, across(!(Request_date_by_week), sum))))


w3<-rbind(w2, colttl)
w3$Request_date_by_week <- as.character(w3$Request_date_by_week)
w3[which(as.Date(w3$Request_date_by_week)==as.Date(0)),]$Request_date_by_week <-"Grand Total"

#rmax <- max(as.numeric(rownames(w3)))

w3 %>%
  #mutate(Total=cell_spec(Total, "html", bold=T, italic = T)) %>%
   knitr::kable(caption="Table 1 Top Companies vs. Others Weekly Volume", escape = FALSE, col.names=c("Week", "American Income", "Northwest Mutual", "Pacific Life", "Protective", "Banner", "Other", "Total"),row.names = FALSE, align="c") %>%
   kable_styling(full_width = F, position = "center", fixed_thead = list(enabled = T, background = "#ccffe6"), bootstrap_options=c("striped", "hover", "condensed", "responsive")) %>%
   column_spec(8, bold = F, border_left = T, background = "ivory") %>%
   row_spec(9, bold= T, italic = T, background = "ivory")

```
_Top 5 companies include American Income, Northewest Mutual, Pacific Life, Protective, and Banner by business decision._


### Weekly Growth


```{r}
lwk <- w2 %>%
     mutate(across(.cols = !(Request_date_by_week), ~lead(.x, n=1L)))

names(lwk)[2:6]<- as.character((lapply(names(lwk[c(2:8)]), function(x) paste(x, "_Pr_Wk", sep = ""))))

grow <- cbind(lwk[1], w2[c(-1)]/lwk[c(-1)]-1)

grow2<- grow %>%
       mutate(across(.cols = !(Request_date_by_week), ~percent_format(accuracy = 0.1)(.x)))

grow2[which(!is.na(grow$Total)),] %>%
  #mutate(Total=cell_spec(Total, "html", bold=T, italic = T)) %>%
   knitr::kable(caption="Table 2 Top Companies vs. Others Weekly Growth", escape = FALSE, col.names=c("Week", "American Income", "Northwest Mutual", "Pacific Life", "Protective", "Banner", "Other", "Total"),row.names = FALSE, align="c") %>%
   kable_styling(full_width = F, position = "center", fixed_thead = list(enabled = T, background = "#ccffe6"), bootstrap_options=c("striped", "hover", "condensed", "responsive")) %>%
   column_spec(8, bold = F, border_left = T, background = "ivory")


```



Row {data-height=600}
-----------------------------------------------------------------------
### Volume Trend


```{r}

ts<- xts(w[, 2:7], as.Date(w$Request_date_by_week))

#volume chart, multiple series
highchart(type="stock", width = 300) %>%
#  hc_xAxis(categories=as.Date(index(ts), format="%Y-%m-%d")) %>%
  hc_title(text="Volume Trend Over Last 8 Weeks", style=(list(fontFamily = "Helvetica")))  %>%
  hc_xAxis(minRange=1) %>%
  # hc_add_series(name="2020", data=ma_xts$MA_CUR, dataLabels =list(enabled = TRUE, format='{point.y:.2f}')) %>%
  hc_add_series(name="American Income", data=ts$American_Income, showInLegend = TRUE) %>%
  hc_add_series(name="Northwest Mutual", data=ts$NWM) %>%
  hc_add_series(name="Pacific Life", data=ts$Pacific_Life) %>%
  hc_add_series(name="Protective", data=ts$Protective) %>%
  hc_add_series(name="Banner", data=ts$Banner) %>%
  hc_add_series(name="Other", data=ts$Other) %>%
  hc_add_theme(thm)

  #
  # hc_annotations(
  #   list(
  #     labelOptions = list(
  #     backgroundColor = 'rgba(255,255,255,0.5)',
  #     verticalAlign = 'top',
  #     y = 10,
  #     shape = "callout",
  #     fill = "none"
  #   ),
  #     labels = list(
  #              list(point = list(x =datetime_to_timestamp(as.Date("2020-04-10")), y = 30000, xAxis = 0, yAxis = 0), text = "2020 Good Friday"),
  #              list(point = list(x = datetime_to_timestamp(as.Date("2020-05-25")), y = 28000, xAxis = 0, yAxis = 0), text = "2020 Memorial Day")
  #     )
  #   )
  # ) %>%
  # hc_tooltip(pointFormat = "<span style=\"color:{series.color}\">{series.name}</span>: {point.y:.2f}") %>%



```


### Growth Trend

```{r}

fn<- function(x) {x*100}
grow3<- grow[which(!is.na(grow$Total)), ] %>%
       mutate(across(.cols = !(Request_date_by_week), ~fn(.x)))

ts2<- xts(grow3[, 2:7], as.Date(grow3$Request_date_by_week))

#volume chart, multiple series
highchart(type="stock") %>%
  # hc_xAxis(categories=as.Date(index(ts2), format="%Y-%m-%d")) %>%
  hc_title(text="% Change in Volume Over Last 8 Weeks", style=(list(fontFamily = "Lucida Sans Unicode")))  %>%
  hc_xAxis(minRange=1) %>%
  hc_yAxis(labels=list(format="{value}%")) %>%
  # hc_add_series(name="2020", data=ma_xts$MA_CUR, dataLabels =list(enabled = TRUE, format='{point.y:.2f}')) %>%
  hc_add_series(name="American Income", data=ts2$American_Income, showInLegend = TRUE) %>%
  hc_add_series(name="Northwest Mutual", data=ts2$NWM) %>%
  hc_add_series(name="Pacific Life", data=ts2$Pacific_Life) %>%
  hc_add_series(name="Protective", data=ts2$Protective) %>%
  hc_add_series(name="Other", data=ts2$Other) %>%
  hc_add_theme(thm) %>%
  hc_tooltip(pointFormat = "<span style=\"color:{series.color}\">{series.name}</span>: {point.y:.2f}%")

  #
  # hc_annotations(
  #   list(
  #     labelOptions = list(
  #     backgroundColor = 'rgba(255,255,255,0.5)',
  #     verticalAlign = 'top',
  #     y = 10,
  #     shape = "callout",
  #     fill = "none"
  #   ),
  #     labels = list(
  #              list(point = list(x =datetime_to_timestamp(as.Date("2020-04-10")), y = 30000, xAxis = 0, yAxis = 0), text = "2020 Good Friday"),
  #              list(point = list(x = datetime_to_timestamp(as.Date("2020-05-25")), y = 28000, xAxis = 0, yAxis = 0), text = "2020 Memorial Day")
  #     )
  #   )
  # ) %>%





```

Row {data-height=900}
-----------------------------------------------------------------------

### Number of Weeks with No Request

```{r}
nrq <- cmb %>%
       select(Company_Name, Company_Symbol, Request_date_by_week) %>%
       group_by(Company_Name, Company_Symbol) %>%
       summarise(minwk=min(Request_date_by_week), maxwk=max(Request_date_by_week)) %>%
       select(Company_Name, Company_Symbol, minwk, maxwk) %>%
       mutate(noreq=(difftime(mwk, maxwk, units = "weeks"))) %>%
       filter(noreq >0) %>%
       arrange(noreq, Company_Name, Company_Symbol)

class(nrq$noreq) <- "num"

nrq %>%
  #mutate(Total=cell_spec(Total, "html", bold=T, italic = T)) %>%
   knitr::kable(caption="Table 3 Companies with No Request in Weeks", escape = FALSE, col.names=c("Company", "Company Symbol", "Start Week", "End Week", "Gap"),row.names = TRUE, align="c") %>%
   kable_styling(full_width = F, position = "center", fixed_thead = list(enabled = T, background = "#ccfff5"), bootstrap_options=c("striped", "hover", "condensed", "responsive")) %>%
   column_spec(6, bold = F, border_left = T, background = "#ffe6e6")

```

### Weekly Volume vs. Growth


```{r}

vg <- cmb %>%
      filter(difftime(mwk, Request_date_by_week, units = "weeks") <=1) %>%
      select(Company_Name, Company_Symbol, Request_date_by_week, `#_request_submitted`) %>%
      group_by(Company_Name, Company_Symbol) %>%
      mutate(Lst_wk_req=lead(`#_request_submitted`, n=1L)) %>%
      mutate(wkly_chg = (`#_request_submitted`/Lst_wk_req)-1) %>%
      filter(Request_date_by_week == mwk) %>%
      arrange(desc(wkly_chg))

vg$wkly_chg_pct <- percent_format(accuracy = 0.1)(vg$wkly_chg)


vg[, !(names(vg) %in% c("Request_date_by_week", "wkly_chg"))] %>%
  #mutate(Total=cell_spec(Total, "html", bold=T, italic = T)) %>%
   knitr::kable(caption="Table 4 Lastest Weekly Volume vs. Weekly Growth by Company", escape = FALSE, col.names=c("Company", "Symbol", "Current Week", "Prior Week", "Growth"),row.names = TRUE, align="c") %>%
   kable_styling(full_width = F, position = "center", fixed_thead = list(enabled = T, background = "#ccfff5"), bootstrap_options=c("striped", "hover", "condensed", "responsive")) %>%
   column_spec(6, bold = F, border_left = T, background = "#ffe6ff")


```

Row {data-height=800}
-----------------------------------------------------------------------

### Volume vs Growth Chart

_Volumes above the average are categorized as large. Changes greater than 0 are categorized as growth._

```{r fig.height=3, fig.width=8, fig.align = "center", out.width='40%'}

wavg <- mean(vg$`#_request_submitted`)

vg$Segment <- ifelse(vg$`#_request_submitted` >= wavg, ifelse(vg$wkly_chg_pct >0, "Large Growing", "Large Not Growing"), ifelse(vg$wkly_chg_pct>0, "Small Growing", "Small Not Growing") )

p <- ggplot(vg[which(!is.na(vg$wkly_chg_pct)),], aes(x=`#_request_submitted`, y=wkly_chg, color=Segment, text=Company_Name)) +
           geom_point(shape=1)+      # Use hollow circles
           labs(
                x = "Current Week Volume",
                y = "Change Over Prior Week",
                color = "Segment") +
           scale_y_continuous(labels = scales::percent_format(accuracy = 1))

ggplotly(p, tooltip = c("text", "color"))
# pp<-ggplotly(p, width=400, height=500)

# library(htmltools)
# ppc <- htmltools::div( pp, align="center" )

```

